%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Thin Formal Letter
% LaTeX Template
% Version 1.11 (8/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% WikiBooks (http://en.wikibooks.org/wiki/LaTeX/Letters)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4


\usepackage{geometry}
\geometry{
	left=3cm,
	right=3cm,
	top=5cm,
}


%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\section{Cover Letter}
\end{center}
\large
I am an image data scientist with a multidisciplinary background. As a PhD computer science researcher, I worked on complex challenging problems on healthcare imaging data. These required mathematical and computational modelling and engineering solutions. The PhD was followed by two full-time research positions at a cardiac surgical lab at Imperial and then at a world-renowned imaging and robotics lab at King's College London. Both have been based in NHS hospitals and working closely with clinical practitioners such as doctors and radiologists. 

I gained over 10 years experience in image data science, cardiac data, medical imaging, devices, AI and biomedical applications. I have strong interpersonal skills obtained by working in teams with researchers of diverse backgrounds, maintaining international collaborations, and supervising junior researchers. Currently, I am a senior researcher at King's College London where I usually lead or co-lead on various projects.

I have demonstrated excellent communication and presentation skills. I have supervised 42 short term projects with students and 18 more longer term projects, coaching and motivating colleagues towards completion. This is the best part of my current role, where I am able to share insights and experience on technical problems in my area of expertise and advise junior researchers. I deliver talks to present my ideas on a regular basis at large meetings and conferences. Most recently, I have organised international data challenge workshops in Barcelona, Nice and Athens, engaging with international collaborators and colleagues. Also, recently I completed a course on leadership. 

I have been actively involved on commercial projects through private consulting. I have worked closely with stakeholders and managing directors, shaping their vision and bringing their ideas to life. Together we created software products that have made businesses more efficient and profitable.

I am looking for a Lead or Senior data scientist role in an established and forward-looking company where I can use my problem solving skills on exciting and diversified projects. My quantitative skills and multidisciplinary background will allow me to work in different industries and sectors such as finance, government, healthcare, telecom, biotechnology, retail, etc. I am very excited about data science and AI. Over the next five years, I am looking to become an expert, and a leader and motivate teams of researchers, engineers and scientists.  


 
\end{document}