%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.0 (14/7/16)
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Vel (vel@LaTeXTemplates.com) and Harsh (harsh.gadgil@gmail.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Originally found on https://www.sharelatex.com/templates/cv-or-resume/smart-twenty-seconds-cv

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4


% Command for printing framework bubbles
\newcommand\modelling{ 
~
	\smartdiagram[bubble diagram]{
        \textbf{Machine}\\\textbf{Learning},
        \textbf{Dim}\\\textbf{reduction},%
        \textbf{Logistic} \\\textbf{regression},
        \textbf{Markov}\\\textbf{chains},
        \textbf{Likelihood}\\\textbf{estimation},
        \textbf{Naive}\\\textbf{Bayes},
        \textbf{Conv}\\\textbf{Nets}
    }
    
}

% Command for printing skill overview bubbles
\newcommand\skills{ 
~
	\smartdiagram[bubble diagram]{
        \textbf{Data}\\\textbf{Analysis},
        \textbf{Full Stack}\\\textbf{Web Dev},
        \textbf{Biomedical} \\\textbf{Engineering},%
        \textbf{Deep}\\\textbf{Learning},
        \textbf{Machine}\\\textbf{Learning},
        \textbf{Image}\\\textbf{recognition},
        \textbf{Statistical}\\\textbf{Analysis}
    }
}

% Programming skill bars
\programming{{Pandas $\textbullet$ Keras  $\textbullet$ VTK / 1}, {JS $\textbullet$ SQL $\textbullet$ \large MATLAB / 2}, {C++ $\textbullet$ PHP $\textbullet$ Python / 5}}


% Projects text
\awards{
\awarditems{2017}{EPSRC early career scientist fellowship top 10 finalist  for £1m}\\[1.5mm]
\awarditems{2016}{Journal of Cardiovascular Imaging highly cited research award}\\[1.5mm]
\awarditems{2015}{Imperial College Honorary Lecturer}\\[1.5mm]
\awarditems{2014}{Medical Engineering UK best paper poster}\\[1.5mm]
\awarditems{2012}{Hamlyn Robotics UK best paper poster}\\[1.5mm]
\awarditems{1998}{University of Toronto Scholar award}\\[1.5mm]

}
\talks{
\\[2mm]

\textit{Recent only}\\[1mm]
\talkitems{2018}{Prediction of pacing sites for cardiac pacemakers, IEEE EMBC}{USA}\\[2mm]
\talkitems{2017}{Visualisation and uncertainty in whole-heart modelling, Zuse Maths Inst.}{Berlin} \\[2mm]
\talkitems{2017}{Problem solving using biomedical imaging analysis, EuroSciCon}{UK} \\[2mm] 
\talkitems{2015}{Data analytics and visualisation in interventional cardiac MRI, SCMR}{France}\\[2mm]
\talkitems{2015}{Quantification algorithms to assess heart attacks from imaging, Hounsfield Lectures}{UK}\\[2mm]
}

\teaching{
\\[1mm]
\textit{Supervised theses (recent)}\\[1mm]
\teachingitems{2017}{Model-based image analysis of cardiac wall thickness using measurements from CT} \\[1mm]
\teachingitems{2017}{Image processing algorithms for measuring wall thickness in CMR} \\[1mm]
\teachingitems{2016}{Tissue contact force sensing in uni and multi-directional catheters} \\[1mm] 
\teachingitems{2016}{Robotic ablation catheter - experimentations on precision and control} \\[1mm]
\teachingitems{2016}{Validation of an adapted Cosserat rod model for contact force estimation} \\[1mm]
\teachingitems{2016}{Ablation path trajectories of a robotic catheter inside a heart phantom} \\[1mm]
\begin{footnotesize}
\textit{Years 2012 - 2016, 12 theses were supervised}\\
\end{footnotesize}
}

\editorial{
\\[1mm]
\editorialitems{J. of Healthcare Engineering}{Editorial board}
\editorialitems{Asian J. of Info. Technology}{Editorial board}
\editorialitems{Trans. Pattern Analy. \& Mach. Intel.}{Reviewer}
\editorialitems{Sensors}{Reviewer}
\editorialitems{IEEE Trans. Medical Imaging}{Reviewer}
}


%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------
% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

\cvname{Rashed Karim} % Your name
\cvjobtitle{ Image Data Scientist } % Job
% title/career

\cvlinkedin{/in/karimphd}
\cvgithub{drkarim}
\cvnumberphone{(44) 79 69 77 03 72} % Phone number
\cvsite{bit.ly/drkarim} % Personal website
\cvscholar{bit.ly/scholarX} % scholar
\cvmail{rashed.karim@gmail.com} % Email address

%----------------------------------------------------------------------------------------



\begin{document}
\makeprofile % Print the sidebar

%----------------------------------------------------------------------------------------
%	 EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem
    	{2005 - 2009}
        {}
        {PhD. Computer Science }
        {\href{http://www.doc.ic.ac.uk/}{Imperial College London}}
        {}
        {}
	\twentyitem
    	{2004 - 2005}
		{}
        {MSc. Advanced Computing \textnormal{(Distinction)}}
        {\href{http://www.qmul.ac.uk/}{Queen Mary, U. of London}}
        {}
        {}
    	\twentyitem
    	{1998 - 2002}
		{}
        {BSc. Computing \& Mathematics}
        {\href{http://www.utoronto.ca/}{University of Toronto, Canada}}
        {}

	%\twentyitem{<dates>}{<title>}{<organization>}{<location>}{<description>}
\end{twenty}


%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{twenty} % Environment for a list with descriptions
\twentyitem
    	{2010 -}
		{Present}
        {Research Fellow}
        {\href{https://kclpure.kcl.ac.uk/portal/rashed.karim.html}{King's College London}}
        {}
        {\begin{itemize}
       \item Making predictions from 3D imaging data using ML and AI. Quantitative analysis of data. Gaining over 10 years' experience in image data analytics. 
\item Published 41 research papers in leading journals and conferences in last 7 years. An authority on cardiac image analysis
\item Co-chaired and organised 3 international data challenges at premier medical imaging conferences
\item Designed software for NHS research units in Leeds \& London. 
\item Commercialisation of technology used for implanting cardiac pacemakers with Siemens Healthcare
\item Long track record of project supervision: 42 individual projects and 18 BSc student projects (13/18 obtained a 1st grade). 
       
        \end{itemize}}
        \\
	\twentyitem
    	{2007 - }
		{Present}
        {Full Stack Development Consulting}
        {\href{http://www.desilvatutors.co.uk/}{Karim Consulting LTD}}
        {}
        {
        {
    \begin{itemize}
\item Architect and full-stack developer of a London agency's cloud-based CRM system in PHP/MySQL ($\approx$30,000 lines of code) 
		\item Work closely with stakeholder and MD of the company on strategic roadmaps for CRM 
    \end{itemize}}
        }
    
    \\   
    \twentyitem
   		{2009 -}
		{2010}
        {Research Associate}
        {\href{http://www.imperial.ac.uk}{Imperial College London}}
        {}
        {
        {\begin{itemize}
        \item Designed software to recognise dead tissue from images, work was published as scientific article and cited 73 times on Google Scholar
    \end{itemize}}
        }
     \\
     \twentyitem
   		{2007 -}
		{2008}
        {Software Developer Intern}
        {\href{http://www.ey.com/}{Ernst and Young London}}
        {}
        {
        \begin{itemize}
        \item Member of infrastructure team, building plug-ins and deploying for EY global. Continued employment after internship. Declined offer of further employment to complete PhD.
        \end{itemize}
     	}   
    \\   
    \twentyitemoneliner{2006}{Game QA analyst Intern}{\href{http://www.glu.com}{Glu Mobile Gaming}}

    	\\ 
      \twentyitem
   		{2003 -}
		{2004}
        {Lecturer in Mathematics}
        {\href{http://www.primeasia.edu.bd/}{Primeasia university, Bangladesh}}
        {
        \begin{itemize}
        \item 1st and 2nd year university-level calculus. Youngest lecturer in university. Resigned from post to pursue further study. 
 
        \end{itemize}
        }{}
	\\ 
      \twentyitem
   		{2002 - }
		{2003}
        {Java developer}
        {\href{https://en.wikipedia.org/wiki/BEA_Systems}{BEA Weblogic Dubai}}
		{
		\begin{itemize}
		\item JSP and Servlets development. Sun Java certified programmer
		\end{itemize}		
		}{}
	\\ 
	 \twentyitemoneliner{2001}{Part-time Tutor in Microprocessor Systems}{\href{https://www.utoronto.ca}{University of Toronto}}
     
        
        
	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}
\input{publication_list}

\end{document}


